---
title: "Lab 03 - Nobel laureates"
author: "Rowan Kemmerly"
date: "1.31.22"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

#### How many observations and how many variables are in the dataset? Use inline code to answer this question. What does each row represent?

```{r dataset-info}
glimpse(nobel)
```

There are 26 columns and 26 corresponding variables, and each of the 935 rows represents an individual Nobel laureate.

### Exercise 2

Now I'm creating the data frame for only currently alive Nobel laureates. 

```{r creating-nobel-living}
nobel_living <- filter(nobel, !is.na(country), gender != "org", is.na(died_date))
```

```{r nobel-living-info}
glimpse(nobel_living)
```


### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
